\chapter[The CMS experiment at LHC]{The CMS experiment at LHC}

The CMS experiment is one of the biggest particle physics experiments on the world. It is located at the ring of the LHC that is the main experience directed by CERN, the European Organization for Nuclear Research or Centre Europ\'{e}enne pour la Recherche Nucl\'{e}aire by its name on french. This center constitutes the biggest center for research on particle physics all over the world. All along its 60 years of existence, from 1954, 21 member states have been joining it, but an overall of 113 countries participate on this center. 

On the present chapter we discuss in detail different aspects of the LHC accelerator and the CMS experiment. In particular we make some emphasis in the CMS sub-detectors related to jets, objects that play the main role on the search that is the main subject of the present work. We also discuss the present state of both machines, their achievements and the challenges that were came through. Finally, also the expectations and goals for the upcoming run II are described.  

\section{The Large Hadron Collider}
\label{sec:LHC}

The Large Hadron Collider, or LHC, is a machine that accelerates and collides protons and heavy ions. This machine is the biggest particle collider nowadays with a circumference of 27 km. It also achieves the greatest energy by a collider up to present, planned to be 14 TeV at the center of mass of the collision. It's located in French-Swiss border near to Geneva. The tunnel for the machine was carved around 100 m under the ground, 45 m under the Jura mountains and 170 m under the L\'{e}man lake with an inclination of around 1.4\%, sloping down towards the lake . This machine has used as much as possible old LEP buildings, that was an electron-positron collider built between 1984 and 1989. 

The protons and heavy ions accelerated by the machine are collided in different points where dedicated experiments are located to detect the product from the collisions. The four main experiments located on the LHC ring are CMS, ATLAS, LHCb and ALICE. The first two are experiments of generic purpose where searches for new physics and also precision measurements are performed. LHCb is dedicated to the physics of the b-quark, while ALICE focuses on the study of the quark-gluon plasma produced from heavy ions collisions. However one of the principal objectives of the construction of the LHC was the discovery of the Higgs boson, generic searches on new physics have been conducted from the very beginning of the first data taking on 2009. Moreover, after the Higgs discovery on 2012 there is a growing effort on the searches for new physics and precision measurement on the properties of the Higgs.


\section{The Compact Muon Solenoid experiment}
\label{sec:CMS}



\[ f'(x) = 1-2x \]
\[ \beta(x) \leq \cos(x) \]
\[ \sqrt{\frac{1}{2}}=\frac{\sqrt(2)}{2} \]

\begin{equation}
\forall x \in \mathbb{R}, f'(x)=f(x)
\end{equation}

\begin{equation}
\lim_{x\to 0}\frac{\sin(x)}{x}=1
\end{equation}

\begin{equation}
\int_{0}^{\infty}\frac{\ln(x)}{f(x)}=\pi^2
\end{equation}

\begin{equation*}
\left\Vert 2^{\Gamma(x)} \right\Vert^{2} = \underbrace{f(a)+f(b)}_{\leq 1}+\dot{y}
\end{equation*}
